Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-27 response/response.tex

% Reviewer 1: Q18
\begin{review}
It is not clear on p. $8$, line $15$, if the size of the database is $380$ megabytes (MB) or $380$ megabits (Mb).
%In the former case "MB" should be used instead of "Mb", while in the latter case the authors should consider reporting the value in megabytes (MB) which is more common.
\end{review}

\begin{response}
It is $380$ MB.
We have changed it in the text.
\end{response}

% Reviewer 1: Q19
\begin{review}
In Eq. $3$, p. $8$, the authors should better define the symbols used.
In particular, it is not clear if subscripts $1$ and $2$ refer to inner and outer leaf tips respectively, and in which order.
\end{review}

\begin{response}
$t_1$ represents the outer leaf tip and $t_2$ represents the inner leaf tip.
This representation is the same as the released leaf tip labels as illustrated in Sec. $4.4$.
The equation does not rely on the correspondence of inner or outer tips as long as the estimated tips correspond to the labeled tips.
\end{response}

@@

% Reviewer 2: Q22
\begin{review}
The authors do a nice work of calibrating the cameras and measuring noise in the depth camera.
However, in page $2$ introduction says that this calibration allows for the explicit correspondence between pixels of any modality.
The authors rely on this to annotate data in one modality and propagate labels in the other (at least this is what I understand from later on description of methodology).
However, this is a VERY strong assumption and depends completely on the distance between the cameras, the angles, the distance between object and sensors and the actual object arrangement.
From our experience even when imaging co-planar plants (such as young Arabidopsis) at a distance of $\sim 70$ cm even when the camera sensors are really close to each other (less than $5$ cm) some differences in view are there and occlusions are present.
The authors should comment on this and should show as supportive evidence examples of plants at different growth stages in all $4$ modalities in raw and annotated form to show how close this correspondence is matching and how the propagated labels.
Furthermore, additional supporting evidence could be obtained either by arranging for two external and blind annotators to label some data (different age, different placement in the tray to show the effect of angle) in another modality (e.g., optical) and then measure inter-observer variability.
Then they can propagate annotations from fluorescence to images of that modality and measure agreement.
If this agreement is better than the in between rater variability then you could argue that propagating annotations is ok to do and actually beneficial.
Nevertheless, you should definitely mention this limitation of your work.
\end{review}

\begin{response}
We add one more section (Sec. $4.3$) in the paper to describe the labeling and the propagation to other modalities. 
The data labeling is performed in the fluorescence image modality.
The infrared image is from the same camera and so pixel labeling will be identical.
The labels are propagated to the RGB color and depth modalities using planar homographies.
The homography between the fluorescence image and the RGB color image is calculated by fitting matching features in these modalities, and the homography to the depth image is found by fitting a plane through the $3$D plant points.
As the reviewer noted, using these homographies will result in pixel segmentation errors due to parallax for plant regions outside of the modeled planes.
We evaluate these errors qualitatively and quantitatively.
Figure $6$ illustrates the label propagations from the fluorescence image to the other modalities and from the color image to other modalities with two different line colors.
Errors occur where the lines fail to overlap and are due to propagation effects as well as boundary selection variations by the labeler between modalities.
We compare the magnitude of these two effects in Table $4$.
The performance of label propagation is only slightly worse than the performance of another annotator.
Therefore, we propagate the fluorescence labels to other modalities for Arabidopsis plants.
As for bean plant, the homograph-based mapping performed poorly due to the large within-plant depth variations.
So we only provide the labels for bean plant in fluorescence and IR as they use the same camera.
Please refer to Sec. $4.3$ for more details.
\end{response}

@@

% Reviewer 2: Q23
\begin{review}
Furthermore, it assumes that cameras are perfectly synchronized which i) is not mentioned and ii) it cannot be done for some modalities since the same camera (with different filter) is used so some delay is expected.
Granted the plants may not move in between but this should be clarified and mentioned.
\end{review}

\begin{response}
We have this clarification in the paper.
In Sec. $3.2.3$, we describes our image collection process, where the capture of all four modalities takes $4$ minutes.
During this short period, no substantial movement or growth were observed.
\end{response}

% Reviewer 2: Q24
\begin{review}
Fig. $3$ (a) ... From Fig. $2$ it appears the distance from plant to sensor to be greater than $60~mm$ ($6~cm$) !!! ie., to me it looks close to $60~cm$, but either Fig. $3$ has wrong axis range or something else is going on.
Can you please explain/update?
Also same Fig. $3$, shouldn't the images overlap?
Why are shown translated?
\end{review}

\begin{response}
Yes, the distance to the plant is roughly $620~mm$.
The image planes are plotted not at the plant location, but at a distance proportional to the focal length of each camera.
We added dashed lines to the figure to make it clearer that these planes do not correspond to the plant depth, and updated the caption to better explain it.
\end{response}

@@

% Reviewer 2: Q29
\begin{review}
Again going back to the problem of lack of exact $1-1$ correspondence between modalities, how can you guarantee that labels on one are good on the other given such high differences in resolutions among modalities?  Please include at least some visual examples.
\end{review}

\begin{response}
Please refer to Comment $22$.
\end{response}

% Reviewer 2: Q30
\begin{review}
Does the annotation $\_$hour$\_$YY$\_$label.png contain a label for each pixel or only for the boundaries?
If yes, then can you obtain single boundary definition in between overlapping leaves?
\end{review}

\begin{response}
The annotated image is an image the same size as the original image.
And each pixel is annotated with a number.
The same number represents the same leaf and $0$ represents the background.
For overlapping leaves, we can visualize the relative location and annotate accordingly.
Please refer to Fig. $9 (b)$ for examples of the labeled images.  
\end{response}

### 2015-07-27 response/response.tex

% Reviewer 2: Q23
\begin{review}
Furthermore, it assumes that cameras are perfectly synchronized which i) is not mentioned and ii) it cannot be done for some modalities since the same camera (with different filter) is used so some delay is expected.
Granted the plants may not move in between but this should be clarified and mentioned.
\end{review}

\begin{response}
We have this clarification in the paper.
In Sec. $3.2.3$, we describes our image collection process, where the capture of all four modalities takes $4$ minutes.
During this short period, no substantial movement or growth were observed.
\end{response}

% Reviewer 2: Q24
\begin{review}
Figure $3$ (a) ... From Figure $2$ it appears the distance from plant to sensor to be greater than $60~mm$ ($6~cm$) !!! ie., to me it looks close to $60~cm$, but either Figure $3$ has wrong axis range or something else is going on.
Can you please explain/update?
Also same Figure $3$, shouldn't the images overlap?
Why are shown translated?
\end{review}

@@

% Reviewer 2: Q29
\begin{review}
Again going back to the problem of lack of exact $1-1$ correspondence between modalities, how can you guarantee that labels on one are good on the other given such high differences in resolutions among modalities?  Please include at least some visual examples.
\end{review}

\begin{response}
Please refer to Comment $22$.
\end{response}

% Reviewer 2: Q30
\begin{review}
Does the annotation $\_$hour$\_$YY$\_$label.png contain a label for each pixel or only for the boundaries?
If yes, then can you obtain single boundary definition in between overlapping leaves?
\end{review}

\begin{response}
The annotated image is an image the same size as the original image.
And each pixel is annotated with a number.
The same number represents the same leaf and $0$ represents the background.
For overlapping leaves, we can visualize the relative location and annotate accordingly.
Please refer to Figure $9 (b)$ for examples of the labeled images.  
\end{response}

### 2015-07-27 datapaper_conclusion.tex
explant conlusion

\section{Conclusions}

This paper presents a newly collected multi-modality plant imagery database, ``MSU-PID''.
Compared to existing databases in the field, MSU-PID not only has multiple calibrated modalities, but also enables a wide variety of plant image analysis applications.
Therefore, we believe this new database will be benefitial to the research community in terms of algorithm development, performance evaluation, and identifying new research problems in plant image analysis.
Furthmore, we are also open to suggestions and comments from the users of this database to further enhance our imaging setup and capturing protocol, so that we can develop new databases in the future.

>>>>

\section{Conclusion and Discussion}

This paper presents a newly collected multi-modality plant imagery dataset ``MSU-PID''.
It has two subsets for Arabidopsis and bean plants respectively. 
Compared to existing databases in the field, MSU-PID uses multiple calibrated modalities including fluorescence, infrared, RGB color, and depth. 
Detailed image capture process and camera calibration are studied. 
We provide our manual labels about leaf tip locations, leaf segments, and leaf consistency over time on fluorescence modality. 
The labels are propagated to other modalities using homograph mapping for Arabidopsis imagery. 
Our annotations enable a wide variety of plant image analysis applications.

It might be noticed that all plants in MSU-PID belong to the same genotype and no treatments applied.
This is because we think a fundamental issue with visual phenotyping, i.e. accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), which importance has being highlighted in Introduction, needs to be solved before expending our goal to define group differences.
The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
We emphasize more in leaf identification and tracking rather than developing methods to define group differences.

For others to use our dataset, we have designed an experimental protocol with various evaluation metrics for different applications.  
To facilitate future research, we apply our automatic multi-leaf segmentation, alignment, and tracking algorithm on the fluorescence and RGB modalities of Arabidopsis imagery, where the labels for RGB modality is provided via label propagation. 
Our methods performs better on fluorescence images than RGB images. 
This is due to three reasons. 
First, the algorithm is originally developed for fluorescence images. 
Second, the resolution of RGB images are much lower than that of fluorescence images. 
Third, the groudtruth labels for RGB images are generated through the mapping of fluorescence labels, which will cause some error. 
We recognize our dataset as very challenging dataset.

We believe this new database will be beneficial to the research community in terms of algorithm development, performance evaluation, and identifying new research problems in plant image analysis.
Furthermore, We are also open to suggestions and comments from the users of this database to further enhance our imaging setup and capturing protocol, so that we can develop new databases in the future.

%This paper presents a newly collected multi-modality plant imagery database, ``MSU-PID''.
%Compared to existing databases in the field, MSU-PID not only has multiple calibrated modalities, but also enables a wide variety of plant image analysis applications.
%Therefore, we believe this new database will be beneficial to the research community in terms of algorithm development, performance evaluation, and identifying new research problems in plant image analysis.
%Furthermore, we are also open to suggestions and comments from the users of this database to further enhance our imaging setup and capturing protocol, so that we can develop new databases in the future.
%
%It might be noticed that all plants (respectively for Arabidopsis and bean) in MSU-PID belong to the same genotype and no treatments applied.
%%This would entail that the proposed dataset cannot be used to investigate computer vision algorithms or imaging modalities in relation to group differences. Could the authors comment on this? This is true. We are not comparing group differences, based on morphology (for example).
%This is because we think a fundamental issue with visual phenotyping, i.e. accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), which importance has being highlighted in Introduction, needs to be solved before expending our goal to define group differences. The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
%%I think that new text we have added more clearly emphasizes leaf identification and tracking over time rather than developing methods/algorithms to define group differences.
%
%
